Understanding Structure and Selectivity in Nanostructured Lyotropic Liquid Crystal Membranes using Molecular Simulations

### 2020-02-13 Ben_Manuscripts/thesis/intro.tex
Intro outline updates

  \section{Industrial Need for Highly Selective Separations}

  \subsection{Desalination}

  \subsection{Separation of Organic Micropollutants}

  \subsection{Recovery of Valuable Dissolved Species}

  \subsection{Breathable Barriers}

@@

@@

@@

@@

>>>>

  \section{Membranes for Selective Separations}

  \begin{itemize}

    \item Membranes are useful separation tools. Cover historical usage
	\item Some discussion of competing separation technologies. 
	\item They are more efficient and have a smaller footprint than thermal distillation.

  \end{itemize}

  \subsection{How Small Molecule Membrane Separations Work}

  \begin{itemize}

    \item Maybe briefly mention ultrafiltration, microfiltration
    \item Overview of reverse osmosis and nanofiltration.
    \item Separation mechanisms (pore flow versus solution diffusion)

  \end{itemize}

  \subsection{Membrane Separation Applications}

  \begin{itemize}
  	\item Desalination
  	\item Separation of Organic Micropollutants
  	\item Recovery of Valuable Dissolved Species
  	\item Breathable Barriers
  \end{itemize}

  \section{Competing Membrane Technologies}

  \subsection{Amorphous Membranes}

  \begin{itemize}

  \item Mostly about the industry standard, thin film composite polyamide membranes.

  \end{itemize}

  \subsection{Nanostructured Membranes}

  \begin{itemize}

  \item Graphene
  \item Carbon nanotubes
  \item zeolites
  \item MOFs (?) %BJC: these have mostly been used for gas separations. But I've seen some work with aqueous. Not sure if worth covering.

  \end{itemize}

@@

  \begin{itemize}

  \item A less studied class of membranes, LLCs, have the potential to outperform competing membranes.

  \end{itemize}

@@

  \begin{itemize}
    \item Ideal geometry for transport
    \item Go through history
    \item Highlight issues with synthesis
    \item Talk about alignment approaches by Xunda Feng.
  \end{itemize}

@@

  \begin{itemize}
    \item Easier to synthesize
    \item History of monomers used
  \end{itemize}

@@

  \begin{itemize}
    \item Why MD?
    \item Why HII phase?
    \item What work has been done already
  \end{itemize}

  Questions to be answered: %BJC: one major question per chapter
  \begin{enumerate}
    %\item How do we build and equilibrate these systems?
    \item What is the nanoscopic structure?
    \item What factors affect solute transport?
    \item Can we estimate macroscopic properties?
    \item How can we learn mechanisms with minimal human intervention?  %BJC: i.e. machine learning methods
  \end{enumerate}
